\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\usepackage{amsfonts}
\usepackage{geometry}

\begin{document}

\begin{minipage}{1\textwidth}
\begin{flushright}
Thomas Keogh\\
70 Boundary Lane\\
Saltney\\
Chester\\
CH4 8LW\\
thk11@aber.ac.uk\\
07539384445
\end{flushright}
\end{minipage}
\begin{minipage}{1\textwidth}
\begin{flushleft}
Mr John Barnes\\
Lead Developer\\
Android Apps Inc.\\
3 High Street\\
Aberystwyth\\
Ceredigion\\
SY23 1JG\\
\vspace{0.6cm}
\end{flushleft}
\end{minipage}

\noindent
Dear Mr Barnes,\\

\textbf{Android Developer/Java Programmer}\\

\noindent
I am writing to apply for the job of Android Developer within your company, i became aware of the vacant position through staff at my University and it is an area i have great interest in. Please find enclosed a copy of my up to date CV with relevant information.\\

\noindent
I am particularly interested in this job as Android development has shaped a lot of my University experience and is an area i feel i perform well in. With both my second and final year major projects being Android based i have built up a good amount of experience with the platform and it is one i have a good deal of passion for. This is partly due to my belief in the mobile format along with my interest in ubiquitous computing which can be seen through my module choices such as 'Ubiquitous Computing' and modules involving design like 'User Centred Design And Human Computer Interaction'.\\

\noindent
Through my time at University i have gathered experience with all of your required technologies such as PHP, SQL and the Android Environment. Furthermore i have used all three to build applications which have been a success. In my Group Project in my second year i was the Lead Developer for an Android application which gathered data on routes and entered them into RDBMS using PHP and SQL.\\

\noindent
I feel that i can benefit the company through my desire to improve and ability to adapt quickly which is always necessary with a company based on fast moving technologies. I also feel that the knowledge i have now will allow me to quickly fit into your team, moving into a small team is something i already have experience with and i understand the effects it can have. \\

\noindent
Thank you for your time and i look forward to hearing from you in the future.\\

\noindent
Yours Sincerely,\\

Thomas Keogh




















\newpage
\begin{center}
\huge
Thomas David Keogh\\
\normalsize
\vspace{0.1cm}
70 Boundary Lane, Saltney, Flintshire, CH4 8LW\\
Mobile: 07539384445; Landline :01244671443; thk11@aber.ac.uk; tomkeogh.com
\end{center}



\noindent
A hard working and motivated Computer Science Finalist attending Aberystwyth University on track for a high 2:1 / First with working experience of Java and Android including personal Dissertation. Now seeking graduate job to build upon current knowledge of the Android platform.\\

\Large
\noindent
Key Achievements and Skills\\
\normalsize
\begin{description}
  \item[Motivated Problem Solver] \hfill \\ Experience with planning out and completing full programming projects to a design specification and solving the issues posed within them. Achieved a first in ‘Program Design, Data Structures And Algorithms’ (75\%).
  \item[Android Experience]\hfill \\ During my time at University i have successfully completed several Android Applications including the writing of SQL and PHP to handle data parsing and entry into a RDBMS.
  \item[Lead Developer]\hfill \\ Within a group project at University  i was the lead developer on an Android project for the production of an application that would allow a user to plot routes and record information related to them. The Application was a success and led to the group receiving a first for their efforts. 
   \item[Responsible Worker ]\hfill \\ I have experience with large amounts of responsibility both through group work and Work Experience. While working at a primary school i was responsible for large numbers of children and their well being. 
    \item[RESTful Development]\hfill \\ Working experience of RESTful applications through the completion of University modules including 'Developing Internet-Based Applications'. Includes the addition of several features to already existing RESTful sites built with ruby on rails.\\
\end{description}


\Large
\noindent
Education\\
\large
\vspace{0.1cm}
\noindent

\textbf{2012 - Present }\\
\normalsize



\begin{center}
Aberystwyth University\\
\vspace{0.1cm}

Computer Science BSc (Hons) Expected Grade – High 2:1 / First\\
Key Modules \\
\vspace{0.2cm}
Major Project - Pending \hspace{3cm} Modelling Persistent Data 74\%\\
\vspace{0.2cm}
The Software Development Life Cycle 71\% \hspace{0.2cm} C++, C And Java Programming Paradigms 70\%\\
\vspace{0.2cm}
Program Design, Data Structures And Algorithms 75\%
\end{center}
\noindent
\large
\newpage
\textbf{2005 - 2012}\\
\normalsize

\begin{center}
St. David's High School\\
\vspace{0.1cm}
A-Levels – Media Studies (B), National Certificate in ICT Level 3(Distinction)\\ Welsh Baccalaureate

AS-Levels – Psychology (B), Physics (D)

GCSE’s – 12 GCSE’s A*-B including Maths (A), ICT(B), National Diploma in ICT Level 2 (Distinction), Science and Additional Science(Both A)\\

\end{center}

\Large	
\noindent
Work Experience\\

\normalsize

\noindent 
\textbf{July 2014 - Present}
\normalsize

\noindent
The Original Garden Care Service, Chester - Assistant - Part Time\\

\noindent
During my time here my responsibilities have varied due to the nature of the job, this ranges from assisting with set up of equipment for tree trimming to basic equipment maintenance. My time here has helped me to really improve my work ethic due to the physically demanding work and the effect poor attitude has within a small team performing that work. \\

\noindent
While working i handle most smaller jobs and help the full time worker to focus on the more skilled jobs. This often includes manual labour but also help with larger jobs like tree removal. \\

\noindent
\textbf{July 2012}

\noindent
Wood Memorial Primary School, Saltney - Classroom Assistant\\

\noindent
Responsibilities included helping young students with their work while focusing on improving their reading ability, i also ran errands for other staff and supervised children. While here I improved my communication skills due to working as a member of a close knit staff as well as experiencing large amounts of responsibility due to the nature of looking after children\\

\noindent
I contributed by taking some of the work load off of the main teacher and allowing them to focus on a smaller groups of children thus increasing their time per student ratio.\\

\noindent
\textbf{July 2009}

\noindent
Elite PC Systems, Chester - Junior Technician \\

\noindent
During my time here i helped  repair PC's with varying problems while communicating with the public to decipher the possible problem. While working here I developed both my communication skills as well as my technical abilities due to responsibilities including the building of PC's and part swaps in already existing PC's.
I also contributed here by performing tasks such as Virus Removal, Software Installation and the general maintenance of PC's.\\

\Large	
\noindent
References\\
\normalsize
Mrs Ceri Williams, Head Teacher. Wood Memorial CP School, Boundary Lane, Saltney, Flintshire, CH4 8SE. 01244 671807, wood\textunderscore memorial\textunderscore cp\textunderscore saltney@flintshire.gov.uk \\
\vspace{0.1cm}\\
\noindent
Michael F Clarke, Personal Tutor, Aberystwyth University, Room:E54A, Llandinam Building, Penglais Campus, Ceredigion, SY23 3DB. +44 (0)1970 628470; mfc5@aber.ac.uk








\end{document}